Type cones of $\b{g}$-vector fans

### 2019-02-05 thirdPaper/draft/typeConeAssociahedra.tex
Created new section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Relations for~$\b{g}$-vectors in~$2$-Calabi--Yau triangulated categories}
%%%%%
\subsection{Setting}\label{sect::setting}
Let~$\field$ be a field.  Let~$\cat$ be a~$\field$-linear triangulated category with suspension functor~$\susp$.  We fix a collection~$\ind(\cat)$ of representatives of isomorphism classes of indecomposable objects of~$\cat$. We will assume the following:
\begin{itemize}
 \item $\cat$ is essentially small (in particular,~$\ind(\cat)$ is a set);
 \item $\cat$ is~$\Hom{}$-finite: for each pair of objects~$X$ and~$Y$, the~$\field$-vector space~$\cat(X,Y)$ is finite-dimensional;
 \item $\cat$ is Krull--Schmidt: the endomorphism algebra of any indecomposable object is local;
 \item $\cat$ is~$2$-Calabi--Yau: for each pair of objects~$X$ and~$Y$, there is an isomorphism of bifunctors
 \[
  \cat(X,\susp Y) \to D\cat(Y,\susp X)
 \]
 where~$D=\Hom{\field}(-,\field)$ is the usual duality of vector spaces;
 \item $\cat$ contains a basic cluster-tilting object~$T=\bigoplus_{i=1}^n T_i$:
 \[
  \textrm{for any object~$X$,} \quad \cat(T, \susp X) = 0 \quad \textrm{if and only if} \quad X\in \add(T),
 \]
 where~$\add(T)$ is the smallest additive full subcategory of~$\cat$ containing the~$T_i$'s and closed under isomorphisms.
\end{itemize}

@@

%%%%
\subsection{Application to~$\b g$-vectors}\label{sect::applications-g-vectors}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Relations for~$\b{g}$-vectors in finite type cluster algebras via~$2$-Calabi--Yau triangulated categories}
%%%%%
\subsection{Setting}\label{sect::setting}
Let~$\field$ be a field.  Let~$\cat$ be a~$\field$-linear triangulated category with suspension functor~$\susp$.  We fix a collection~$\ind(\cat)$ of representatives of isomorphism classes of indecomposable objects of~$\cat$. We will assume the following:
\begin{itemize}
 \item $\cat$ is essentially small (in particular,~$\ind(\cat)$ is a set);
 \item $\cat$ is~$\Hom{}$-finite: for each pair of objects~$X$ and~$Y$, the~$\field$-vector space~$\cat(X,Y)$ is finite-dimensional;
 \item $\cat$ is Krull--Schmidt: the endomorphism algebra of any indecomposable object is local;
 \item $\cat$ is~$2$-Calabi--Yau: for each pair of objects~$X$ and~$Y$, there is an isomorphism of bifunctors
 \[
  \cat(X,\susp Y) \to D\cat(Y,\susp X)
 \]
 where~$D=\Hom{\field}(-,\field)$ is the usual duality of vector spaces;
 \item $\cat$ contains a basic cluster-tilting object~$T=\bigoplus_{i=1}^n T_i$:
 \[
  \textrm{for any object~$X$,} \quad \cat(T, \susp X) = 0 \quad \textrm{if and only if} \quad X\in \add(T),
 \]
 where~$\add(T)$ is the smallest additive full subcategory of~$\cat$ containing the~$T_i$'s and closed under isomorphisms.
\end{itemize}

@@

%%%%
\subsection{Application to~$\b g$-vectors of cluster algebras of finite type}\label{sect::applications-g-vectors}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Relations for~$\b{g}$-vectors in brick algebras via extriangulated categories}

%%%%
\subsection{Setting}

%%%%
\subsection{Statement of the theorem}

%%%%
\subsection{Proof of Theorem~\ref{}}

%%%%
\subsection{Application to~$\b g$-vectors of brick algebras}

%%%%
\subsection{Examples}

%%
\subsubsection{A brick algebra}

%%
\subsubsection{A quotient of a Frobenius category}
